Instructions for ACL 2020 Proceedings

### 2019-12-02 reports/ACL2020 Paper/acl2020-paper.tex
Update paper outline
add experiment 2 text

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

\section{Background}
%  - dialogue acts
%  - laughter
%  - BERT

\section{Related work}
%  - BERT domain transfer
%  - BERT/LM for DAR

\section{Data}
%  - AMI, SWBD + comparison table
%  - Laughter with/without

\section{Model}
%  - DAR model -> utt encoder, RNN sequence tagger
%  - BERT encoder (12 heads, uncased,...)
%  - baseline encoder

\section{Experiments}
%  - BERT vs. baseline (L/NL)
%  - in-domain pre-training (L/NL)
%  - cross-domain pre-training

\section{Results and discussion}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepackage{booktabs}

@@

\paragraph{Fine-tuning and laughter}
Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
We find that although \%4.6 of utterances in SWDA contain laughter, \%7.3 of utterances misclassified by \texttt{BERT} but correctly classified by \texttt{BERT-FT} contain laughter, suggesting that the fine-tuned model utterance encoder is making use of laughter. 
For AMI-DA, the effect is less pronounced, but still present§: \%8.5 of utterances contain laughter, and \%9.6 of utterances where fine-tuning makes a difference contain laughter.

\section{Background} % Vlad
%  - dialogue acts
%  - laughter
%  - BERT

\section{Related work} % add references first
%  - BERT domain transfer
%  - BERT/LM for DAR

\section{Data}
% - DA distribution              % Vlad
% - Laughter frequencies per DA  % Vlad
% - AMI, SWBD + comparison table % Bill
% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

\section{Model} % Bill
%  - DAR model -> utt encoder, RNN sequence tagger
%  - BERT encoder (12 heads, uncased,...)
%  - baseline encoder

\section{Experiments}
\subsection{Experiment 1: Impact of laughter}   % Vlad
% per dialogue act analysis
% compare impacts of CNN vs BERT
% for both AMI and SWDA

\subsection{Experiment 2: Impact of pre-training} % Bill
% - compare i) pre-trained BERT with freezing ii) pretrained with no freezing iii) randolmly initialized
Next, we take a direct look at how pre-training affects BERT's performance as an utterance encoder for our DAR model.
In particular, we consider the performance of DAR models with three different utterance encoders:
\begin{itemize}
  \item \texttt{BERT} -- pre-trained BERT without fine-tuning (frozen during DAR training)
  \item \texttt{BERT-FT} -- pre-trained BERT with fine-tuninig 
  \item \texttt{BERT-RI} -- randomly initialized BERT with fine-tuning 
\end{itemize}

\begin{table}[]
\centering 
\begin{tabular}{@{}lll@{}}
\toprule
                 & SWDA  & AMI-DA \\ \midrule
\texttt{BERT}       & 55.61 & 46.59  \\
\texttt{BERT-FT}    & 76.93 & 66.94  \\
\texttt{BERT-RI}    & 73.80 & 61.53  
\end{tabular}
  \caption{Micro-average DAR accuracy}
  \label{table:exp2-avg}
\end{table}

The pre-trained model performs better than the randomly initialized model by several percentage points on both DA corpora (table \ref{table:exp2-avg}). 
These results suggest that BERT's extensive pre-training do provide some useful information for dialogue act recoginition.
However, we note that pre-training is not enough: the poor performance of the frozen \texttt{BERT} model indicates that fine-tuning is important for BERT's performance as an utterance encoder.
These observations raise two questions.
First, how does BERT's pre-training help with DAR? 
And second, in what way are the representations learned by pre-trained BERT lacking?
In other words, what is the contribution of fine-tuning?

To help answer these questions, we compare accuracy results of the above three models by dialogue act tag.

% TODO: add per dialogue act accuracy figures

\subsection{Experiment 3: Impact of dialogue pre-training} % Bill
% - pre-train AMI+SWBD -> train SWDA/AMI-DA -> test SWDA/AMI-DA
% - pre-traing tasks: 1) next utterance, 2) masked token, 3) both ?
% - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)

\subsection{Experiment 4: Cross-domain pre-training (if time permits)} % Bill
%  - cross-domain pre-training

\section{Discussion} % add items to discuss
